### 2025-04-21 download-football-data.qmd
20250421 - nflfastR package and target share

Below, we provide examples for how to download various types of NFL data using the `nflreadr` package [@R-nflreadr].
For additional resources, @Congelio2023 provides a helpful introductory text for working with NFL data in `R`.
We save each data file after downloading it, so we can use the data in subsequent chapters.
If you have difficulty downloading the data files using the `nflreadr` package [@R-nflreadr], we also saved the data files so they are publicly available on the Open Science Framework: <https://osf.io/z6pg4>.

@@

First, we can compute the players' season-by-season statistics.

>>>>

Below, we provide examples for how to download various types of NFL data using the `nflreadr` [@R-nflreadr] and `nflfastR` [@R-nflfastR] packages.
For additional resources, @Congelio2023 provides a helpful introductory text for working with NFL data in `R`.
We save each data file after downloading it, so we can use the data in subsequent chapters.
If you have difficulty downloading the data files using the `nflreadr` [@R-nflreadr] or `nflfastR` [@R-nflfastR] packages, we also saved the data files so they are publicly available on the Open Science Framework: <https://osf.io/z6pg4>.

@@

First, we can compute the players' season-by-season statistics using the `nflfastR` [@R-nflfastR] package.

### 2025-04-21 multiple-regression.qmd
20250421 - nflfastR package and target share

@@

We could also generate the model-implied prediction of fantasy points for any value of the [predictor variables](#sec-correlationalStudy).
For instance, here are the number of fantasy points expected for a Wide Receiver who is 23 years old, is 6'2" tall (72 inches), weighs 200 pounds, and has a 3% target share:

>>>>

On a weekly basis, target share is computed as the number of targets a player receives divided by the team's total number of targets.
It would be nice to compute it this way for seasonal data, as well; however, for calculating seasonal target share, the `nflfastR` [@R-nflfastR] package currently sums up the player's weekly target share.
Thus, seasonal target share (unlike weekly target share)—as it is currently calculated—does not range from 0–1.
For example, if a player has a weekly target share of 15%, that would be a seasonal (cross-week-summed) target share of 2.55 ($0.15 \times 17 \; \text{games} = 2.55$.

@@

We could also generate the model-implied prediction of fantasy points for any value of the [predictor variables](#sec-correlationalStudy).
For instance, here are the number of fantasy points expected for a Wide Receiver who is 23 years old, is 6'2" tall (72 inches), weighs 200 pounds, and has a (cross-week-summed) target share of 3 (which reflects an approximate target share of 17.6% percent per game; i.e., $0.176 = \frac{3}{17 \; \text{games}}$):
